AA Distributed Software Development Methodology

### 2013-02-18 front-matter.tex
address improved

\author{%
Renato~Fabbri \and Ricardo~Fabbri \and Vilson Vieira \and Alexandre Negr\~{a}o \and Lucas Zambianchi
\and Marcos Mendon\c{c}a \and Danilo Shiga\\[1em]
\small{
Instituto de F\'{i}sica de S\~{a}o Carlos (IFSC), Universidade de
S\~{a}o Paulo (USP), Brazil}\\[1em]
\small{Instituto Polit\'{e}cnico da Universidade do Estado do Rio de
Janeiro, Nova Friburgo, RJ, Brazil}\\[1em]
\url{LabMacambira.sourceforge.net}.
}

>>>>

\author{%
Renato~Fabbri \and Ricardo~Fabbri \and Vilson Vieira \and Alexandre Negr\~{a}o \and Lucas Zambianchi
\and Marcos Mendon\c{c}a \and Danilo Shiga\\[1em]
\small{
Instituto de F\'{i}sica de S\~{a}o Carlos (IFSC), Universidade de
S\~{a}o Paulo (USP), Brazil}\\[0.5em]
\small{Instituto Polit\'{e}cnico, Universidade do Estado do Rio de
Janeiro, Nova Friburgo, RJ, Brazil}\\[0.5em]
\url{LabMacambira.sourceforge.net}.
}
